Source Summaries

### 2020-04-05 paper/sourceSummaries/summary6.tex
added summary and fixed a bib issues

\noindent
\subsection{{L}ock {P}icking in the {E}ra of {I}nternet of {T}hings}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{8887393}

@@

\noindent
The authors perform a security analysis of a common Bluetooth Smart Lock created by a major brand.  A MasterLock was chosen because of the strong brand recognition in the lock segment, with a smaller emphasis on IOT devices.

@@

\noindent
Game Theory.  The authors perform an attack on a common lock in order to determine inherent weaknesses in the product.

@@

\noindent
The authors conducted an analysis on the backend server API calls.  They do this by reverse engineering the mobile application for the product.  From there, valid requests were sent to determine how the API server would handle various different scenarios.

@@

\noindent
The authors found that guest and master codes are statically generated, meaning that they could not be revoked.  The authors also found that many APIs could be misused to generate unliimited future access codes from the perspectie of a limited guest account.

@@

\noindent
The authors discuss the possibility of investigating the bluetooth connection between the lock and the phone.  Although a limited amount of bluetooth research was done in the authors' testing, a lot more work can be done in investigating the bluetooth link, particularly on guest accounts.

@@

\noindent
\subsection{{I}nvestigations of {P}ower {A}nalysis {A}ttacks on {S}martcards}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{messerges_dabbish_sloan_1999}

@@

\noindent
The main idea of this paper is to analyze power anylysis techniques that had been used in the past to attack the DES encryption protocol. The authors then propose a method to model the signal vs noise ratio.

@@

\noindent
The main theory on display during this analysis is game theory, the authors treat the ability to measue power levels from the reader as a win in this scenario.

@@

\noindent
The authors were able to measure the power dissipation of the smartcard by reading from the ground pin with the assisstance of a small resistor in series between the VSS pin on the card and the true ground.

@@

\noindent
The authors confimed "that power analysis attacks can be quite powerful and need to be addressed." They also were able to successfully propose a way to model the noise characteristics of the power signal coming from the smartcard in hopes of inspiring future work to secure smartcard software against power analysis attacks.

@@

\noindent
The authors suggest that "Future research in this area will investigate power analysis attacks on hardware encryption devices and publickey cryptosystems." At the time this paper was written, AES had not yet been published so there definately room for more work on this topic.

@@

\noindent
\subsection{Poster: Power Replay Attack in Electronic Door Locks}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{seongyeolPoster}

@@

\noindent
The authors theorize that electronic door locks are susceptible to a power replay attack in which an insider modifies the lock with a bypass circuit.  This circuit can be triggered to provide power to the locking mechanism and unlock the door remotely.

@@

\noindent
The theory shown is game theory, if the lock is susceptible to this attack then it is bypassable and considered insecure.

@@

\noindent
The authors attached a Bluetooth capable circuit and LiPo battery to the internal circuitry of the lock.  This is wired in parallel with the original locking circuit so that the lock will still perform normally while the implant is in place.

@@

\noindent
The authors found that locks from the manufacturers Gateman, Samsung, Mille, and Hyegang are susceptible to this attack.  A malicious insider could place these implants without being detected and use it to gain access at a later date.

@@

\noindent
The authors recommend adding tamper detection circuitry to the locks in order to detect if they have been opened along with additional hardware to detect changes in the internal capacitance.  These modifications would make it harder to place an implant like this and allow for an easier detection of an existing implant.

>>>>

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

\noindent
\subsection{Portable RFID Bumping Device}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{dijkPortableBumping}

@@

\noindent
The authors proposed that RFID cards may be vulnerable to a high speed cloning attack performed by bumping into the target.  They posit that this attach can be used to gain clones of security cards without the target's knowledge or raising suspicion.

@@

\noindent
Game Theory.  By showing the ease of cloning the cards the authors show that they are broken and need increased security in order to stay useful.

@@

\noindent
The authors used a Proxmark 3, a LG Nexus 5 with Nethunter, a Hirose usb cable, MIFARE Classic 1K, and MIFARE Classic EV1 1K.  The authors wrote a default key to the cards and then a large number of random keys.  They then generated a large number of random keys to try and gathered a large number of nonces to perform their attack.

@@

\noindent
The authors found that the HF Hirose Antenna increased the range to 6-8cm.  They also successfully implemented BTWA to read multiple cards.  The attacks against the cards were successefully performed against both the Classic and the Classic EV1.

@@

\noindent
The authors posit that more research can be done into the maximum number of cards that can be read at one time.  They also believes that the attack framework can be extended to support more attacks, optimization can be performed on the keyspace calculation software, attempts can be made to try the attack in an unstable environment, and finally optimazation of the Proxmark firmware.
